Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-05-13 closed_loop_planning.tex
[MGa] to handle this...

To handle this, we introduce a \emph{minimal control vector} \(\tilde{\bu} = [F_x\;\; \delta]^T \in \mathbb{R}^2\), where \(F_x\) represents the net longitudinal force. The full control vector $\bu$ is then recovered via a state-dependent linear transformation $
\bu = \bH(\tilde{\bu}) \tilde{\bu}$ with
\begin{equation} \label{eq:minimalcontrol}
\bH(\tilde{\bu}) =
\begin{bmatrix}
\Ipos{F_x} & 0 \\
\Ineg{F_x} & 0 \\
0 & 1
\end{bmatrix}, \quad
\Ipos{x} :=
\begin{cases}
1, & \text{if } x \geq 0 \\
0, & \text{if } x < 0
\end{cases}, \quad
\Ineg{x} :=
\begin{cases}
0, & \text{if } x \geq 0 \\
1, & \text{if } x < 0
\end{cases}.
\end{equation}

@@

To correctly enforce the mutual exclusivity within the LQR synthesis via Riccati recursion, the state-feedback gain must be computed with respect to the minimal control input. Specifically, the control input matrix $\tbB$ is employed and the gain $\tilde{\bK} \in \mathbb{R}^{2 \times 6}$ is sought for which operates on the independent variation \(\delta\tilde{\bu}\). This is structured as
\[
\tilde{\bK} = \begin{bmatrix} \tilde{\bK}_F^T & \tilde{\bK}_\delta^T \end{bmatrix}^T, \quad \tilde{\bK}_F, \tilde{\bK}_\delta \in \mathbb{R}^{1 \times 6}.
\]
The extended gain $\bK$ is automatically recovered via $\bK = \bH \tbK$ and, depending on the operating mode, it will result in the following expressions:
\begin{itemize}
  \item during \emph{acceleration}: \(\bK = \begin{bmatrix} \tilde{\bK}_F^T & \mathbf{0}^T & \tilde{\bK}_\delta^T \end{bmatrix}^T\),
  \item during \emph{braking}: \(\bK = \begin{bmatrix} \mathbf{0}^T & \tilde{\bK}_F^T & \tilde{\bK}_\delta^T \end{bmatrix}^T\).
\end{itemize}
This construction ensures consistency with the complementarity constraint, while maintaining a tractable structure for controller synthesis.

>>>>

To ensure physical consistency while preserving a tractable control structure, we introduce a \emph{minimal control vector} \(\tilde{\bu} = [F_x\;\; \delta]^T \in \mathbb{R}^2\), where \(F_x\) represents the net longitudinal force. The full control vector $\bu$ is then recovered via a state-dependent linear transformation $
\bu = \bH(\tilde{\bu}) \tilde{\bu}$ with
\begin{equation} \label{eq:minimalcontrol}
\bH(\tilde{\bu}) =
\begin{bmatrix}
\Ipos{F_x} & 0 \\
\Ineg{F_x} & 0 \\
0 & 1
\end{bmatrix}, \quad
\Ipos{x} :=
\begin{cases}
1, & \text{if } x \geq 0 \\
0, & \text{if } x < 0
\end{cases}, \quad
\Ineg{x} :=
\begin{cases}
0, & \text{if } x \geq 0 \\
1, & \text{if } x < 0
\end{cases}.
\end{equation}

@@

To correctly enforce the mutual exclusivity within the LQR synthesis via Riccati recursion, the state-feedback gain must be computed with respect to the minimal control input. Specifically, the control input matrix $\tbB$ is employed and the gain $\tilde{\bK} \in \mathbb{R}^{2 \times 6}$ is sought for which operates on the independent variation \(\delta\tilde{\bu}\). This is structured as
\[
\tilde{\bK} = \begin{bmatrix} \tilde{\bK}_F^T & \tilde{\bK}_\delta^T \end{bmatrix}^T, \quad \tilde{\bK}_F, \tilde{\bK}_\delta \in \mathbb{R}^{1 \times 6}.
\]
The extended gain $\bK$ is automatically recovered via $\bK = \bH \tbK$ and, depending on the operating mode, it will result in the following expressions:
\begin{itemize}
  \item during \emph{acceleration}: \(\bK = \begin{bmatrix} \tilde{\bK}_F^T & \mathbf{0}^T & \tilde{\bK}_\delta^T \end{bmatrix}^T\),
  \item during \emph{braking}: \(\bK = \begin{bmatrix} \mathbf{0}^T & \tilde{\bK}_F^T & \tilde{\bK}_\delta^T \end{bmatrix}^T\).
\end{itemize}
This formulation preserves consistency with the complementarity constraint while retaining a structure amenable to controller synthesis.
